\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}


First and foremost, I would like to express my gratitude to Allah the Almighty for giving me the strength and patience necessary to complete this project.

I would like to extend my sincerest thanks to my supervisor, Mrs. Charifa HANIN, for her competent assistance, patience, and encouragement. Her critical feedback has been invaluable in structuring my work and improving the quality of its various sections.

I also want to express my appreciation to my mentor, Mr. AJA Amine, for his immense support, the quality of his guidance, and for all the advice and information he provided with unmatched professionalism and patience.

A big thank you is also owed to Mr. MOUSTACHI Mouhsine, for offering me the opportunity to join his team and for his support.

I would also like to thank Mr. EDDAHBY Mohamed Amine, Mr. ECHARJI Abderrahman, Mr. OUCHEN Othman, Mr. EL ALJ Mohamed Taieb, Mr. EL IDRISSI Hicham, Ms. EL IBRAHIMI Dounia, Mr. OUADHDHAFE Marouane, and all the engineers in the DevOps team for their invaluable assistance, encouragement, and for making my internship at Orange Business a very enriching experience.

I wish to express my sincere gratitude to the members of the jury for the honor they bestow upon me by taking the time to read and evaluate my work.

I would also like to thank the pedagogical and administrative team at INPT for their dedication and contribution to our excellent education.

Finally, I would like to thank all the individuals who have contributed, directly or indirectly, to the completion of this work.